Procrastination Tendencies of Company Corp. Customers

### 2017-12-02 Code/MSDS_CaseStudy2_Master.Rmd
Upload new Master RMD, MD and HTML

---
title: "Procrastination Tendencies of Company Corp. Customers"
date: "November 29, 2017"
output:
  word_document: default
  pdf_document: default
  html_document:
    keep_md: yes
authors: Jose Torres and Lisa Street
---

@@

```{r Question4_Preliminary_Analysis2, warning=FALSE}

@@

```{r Question4_Preliminary_Analysis3, warning=FALSE}

@@

```{r Question5_Preliminary_Analysis}

>>>>

---
title: "Procrastination Tendencies of Company Corp. Customers"
date: "November 29, 2017"
output:
  html_document:
    keep_md: true
authors: Jose Torres and Lisa Street
---

@@

```{r Question4_Preliminary_Analysis2, warning=FALSE,echo=TRUE}

@@

```{r Question4_Preliminary_Analysis3, warning=FALSE,echo=TRUE}

@@

```{r Question5_Preliminary_Analysis,echo=TRUE}
